Reduced MHD Manuscript

### 2024-12-29 Manuscript/Manuscript.tex
Edits

@@

The pressure term gives 
\begin{align*}
    \nabla p\pth{\rho} &= \frac{p_0}{a}\np\pi\pth{1+\ep r} + \bm{e}_Z \frac{2\pi p_0}{L}\p_Z\pi.
\end{align*}

\begin{align*}
    \frac{a}{t_0v_0}\frac{\rho_0v_0^2}{\mu_0^{-1}B_0^2} \pth{1+\ep r} \deriv{\bm{\nu}}{\tau} = M_0^2\beta_0 \pth{1+\ep r} \deriv{\bm{\nu}}{\tau} &= \frac{1}{B_0^2} \pth{a\nabla\times\bm{B}}\times\bm{B} - \beta_0 a\nabla\pi - M_0^2\beta_0 \bm{\nu}\cdot a\nabla\bm{\nu}. 
\end{align*}
where we've multiplied through by $a/\mu_0^{-1}B_0^2$ to make use of orderings. $a\nabla = \np + \ep\bm{e}_Z\p_Z$ makes things easier too.

>>>>

{\color{red} I should write it this way: 
\begin{align*}
    \rho &= \rho_0 \pth{1+\ep r} \\
    \bm{v} &= v_0 \bm{\nu} = v_0 \pmat{\nu_X \\ \nu_Y \\ \nu_Z} = v_0 \pmat{\bm{\nu}_\perp \\ \nu_Z} \\ 
    \bm{B} &= B_0 \bm{\beta} = B_0 \pmat{\ep\beta_X \\ \ep\beta_Y \\ 1+\ep\beta_\para} = B_0 \pmat{\ep\bm{\beta}_\perp \\ \beta_Z},
\end{align*}
Why do I have $\nu_\para$ instead of $\nu_Z$? Why does $\bm{\beta}_\perp$ not include the $\ep$?}

@@

The second and third terms are just   
\begin{align*}
    a\nabla p &= p_0\pth{\np\pi + \ep\bm{e}_Z\p_Z\pi}, \quad\text{and} \\ 
    \rho\bm{v}\cdot a\nabla\bm{v} &= \rho_0v_0^2 \pth{1+\ep r} \pth{\bm{\nu}_\perp\cdot\np\bm{\nu} + \ep\nu_\para\p_Z\bm{\nu}}. 
\end{align*}
Altogether, removing a factor of $\pth{1+\ep r} \rho_0v_0/t_0$ from both sides, we have evolution equations for the dimensionless velocity fields $\nu_\para$ and $\bm{\nu}_\perp$:  
\begin{align*}
    \pth{1+\ep r} \deriv{\nu_\para}{\tau} &= \ep^2 \frac{t_0v_0}{a} \frac{\mu_0^{-1} B_0^2}{\rho_0v_0^2} \pth{\bm{\beta}_\perp\cdot\np\beta_\para + \bm{\beta}_\perp\cdot\p_Z\bm{\beta}_\perp} - \ep\frac{t_0v_0}{a}\frac{p_0}{\rho_0v_0^2} \p_Z\pi - \frac{t_0v_0}{a} \pth{1+\ep r} \pth{\bm{\nu}_\perp \cdot \np\nu_\para + \ep \nu_\para\p_Z\nu_\para} \\ 
    &= \ep^2\frac{1}{M_0^2\beta_0} \pth{\bm{\beta}_\perp\cdot\np\beta_\para + \ep\bm{\beta}_\perp\cdot\p_Z\bm{\beta}_\perp} - \ep \frac{1}{M_0^2\beta_0} \beta_0\p_Z\pi - \pth{1+\ep r} \pth{\bm{\nu}_\perp\cdot\np\nu_\para + \ep \nu_\para\p_Z\nu_\para}. 
\end{align*}
\begin{align*}
    \deriv{\bm{\nu}_\perp}{\tau} &= 
\end{align*}
